Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
further reformulations
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@585 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In the second step, we use our simulation to reproduce the displacements values measured experimentally in~\cite{Hollenstein2006,Nava2008}.
Since the Young's moduli of neither parenchyma ($E_p$) nor capsule ($E_c$ were specified, we obtained both as follows: first, 
performed a set of simulations without the capsule for different values of ($E_p$): the value that provided a good match 
with reported displacement after applying the negative pressure of 30\,kPa inside the tube was $E_p$=30\,kPa. 
The, we fixed the thickness of the capsule as $T$=93\,$\mu$m (reported as an average in the paper) and 
using $E_p$=30\,kPa, we performed repeatedly the simulation with the capsule using different values of the Young's modulus
of the capsule in order to minimize the displacement error. The minimal error (under 1\%) was obtained 
for Young's modulus $E_c$=3\,MPa which lies in the range of capsule elasticity reported by experimental measurements.

@@

Our goal is to create complete liver model suitable for real-time medical
simulations. For this a model accounting for all three main constituents
(parenchyma, vascularization and capsule) is necessary. To achieve that we have
integrated our model with the vasularization method proposed
in~\cite{Peterlik2012}. Adding the capsule did not signifficantly affect the
performance since simulation speed of \TODO{XX FPS}%
\footnote{\TODO{Measured on...}} was achieved. This suggests
that the proposed technique is compatible with real-time simulation of whole
organ while modeling the local properties accurately.

>>>>

In the second step, we employed the simulation to reproduce the displacements values obtained via simulation in~\cite{Hollenstein2006,Nava2008}.
Whereas the simulation in the referenced work was done on a mesh composed of tetrahedral elements for both the parenchyma 
and the capsule, we modelled the capsule using the triangular elements as shown in section~\ref{}.

Since the Young's moduli of neither parenchyma ($E_p$) nor capsule ($E_c$ were specified exactly, we obtained both as follows: first, 
we performed a set of simulations without the capsule for different values of $E_p$: the value that provided a good match 
with reported displacements was $E_p$=30\,kPa. 
Then, we fixed the thickness of the capsule to be $T$=93\,$\mu$m (reported as the average value in the paper) and 
using $E_p$=30\,kPa, we ran the simulation repeatedly using the model with the capsule. In each simulation we 
used different value $E_c$ of the Young's modulus for the capsule in order to minimize the displacement error w.r.t. the 
reported values. The minimal value of error (not exceeding 1\%) was obtained for $E_c$=3\,MPa. This 
value lies in the range of capsule elasticity coefficients reported by experimental measurements.

@@

In the scenario presented in this paper, we focus on local influence of the capsule.
Nevertheless, it is possible to employ the actual model to demonstrate the global 
impact of the capsule and to further validate the accuracy of such a complete model w.r.t. experimental measures. 
Detailed description of such validation is however beyond the scope of this paper. 
In spite of this we would like to emphasize that we have already integrated the
capsule model with vascularized liver model described in~\cite{Peterlik2012}. 
Adding the capsule did not affect the
performance significantly: a visual refresh rate exceeding 25\,FPS was achieved on a
PC with CPU Intel CPU i7-2630QM running at 3.00 GHz.
This suggests that the proposed technique is compatible with real-time simulation of whole
organ while modeling the local properties accurately.
